How to \emph{not} write Virtual Machines for Dynamic Languages

### 2007-07-24 talk/dyla2007/talk.tex
use "general-purpose OO VM" a few times

\begin{frame}
  \frametitle{Implementing Languages on Top of OO VMs}
  \begin{itemize}
  \item
    users wish to have easy interoperation with the OO VMs used by the industry
    (JVM, CLR)
  \item
    bridges don't work that well (XXX maybe skip this)
  \item
    therefore re-implementations of the language on the OO VMs are started
  \item
    even more implementation proliferation
  \item
    implementing on top of an OO VM has its own set of problems
  \end{itemize}
  \pause
  \begin{block}{
    Python Case}
    \begin{itemize}
    \item
      \alert{Jython} is a Python-to-Java-bytecode compiler
    \item
      \alert{IronPython} is a Python-to-CLR-bytecode compiler
    \item
      both are slightly incompatible with the newest CPython version (especially
      Jython)
    \end{itemize}
  \end{block}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Implementing Languages on Top of General-Purpose OO VMs}
  \begin{itemize}
  \item
    users wish to have easy interoperation with the general-purpose OO VMs used
    by the industry (JVM, CLR)
  \item
    therefore re-implementations of the language on the OO VMs are started
  \item
    even more implementation proliferation
  \item
    implementing on top of an OO VM has its own set of problems
  \end{itemize}
  \pause
  \begin{block}{
    Python Case}
    \begin{itemize}
    \item
      \alert{Jython} is a Python-to-Java-bytecode compiler
    \item
      \alert{IronPython} is a Python-to-CLR-bytecode compiler
    \item
      both are slightly incompatible with the newest CPython version (especially
      Jython)
    \end{itemize}
  \end{block}
\end{frame}
